Enforced Invariant Confluence

### 2020-01-19 doc/the_vldb_journal_paper/sections/conclusion.tex
Typo fixes.

\textbf{Acknowledgments.}
The authors would like to thank Alan Fekete, Peter Alvaro, Alvin Cheung,
Alexandra Meliou, Anthony Tan, and Cristina Teodoropol for fruitful discussion
and feedback.
%
This research is supported in part by DHS Award HSHQDC-16-3-00083, NSF CISE
Expeditions Award CCF-1139158, and gifts from Alibaba, Amazon Web Services, Ant
Financial, CapitalOne, Ericsson, GE, Google, Huawei, Intel, IBM, Microsoft,
Scotiabank, Splunk and VMware.

>>>>

\textbf{Acknowledgments.}
The authors would like to thank Alan Fekete, Alexandra Meliou, Alvin Cheung,
Anthony Tan, Cristina Teodoropol, Peter Alvaro, and Peter Bailis, for fruitful
discussion and feedback.
%
This research is supported in part by DHS Award HSHQDC-16-3-00083, NSF CISE
Expeditions Award CCF-1139158, and gifts from Alibaba, Amazon Web Services, Ant
Financial, CapitalOne, Ericsson, GE, Google, Huawei, Intel, IBM, Microsoft,
Scotiabank, Splunk and VMware.

### 2020-01-19 doc/the_vldb_journal_paper/sections/merge_reduction.tex
Typo fixes.

An illustration of this proof is given in \figref{DiamondProofDiagram}. We
arrange the expressions $e_1$ and $e_2$ as the left and top edges of a square
grid. Each point in the grid represents a state (with $s_0$ in the top left
corner), and each edge represents the application of a transaction. A state is
circled if we know it satisfies the invariant.
%
Condition (1) and (2) tell us that the order in which we apply transactions is
immaterial. Thus, if we begin at the top left of the square and walk to any
other point in the square, applying transactions along the way, it does not
matter which path we take. They are all equivalent. Condition (4) tells us that
the top-left corner satisfies the invariant. We induct to repeatedly apply
condition (3) to ``fill in'' the square, one block at a time. In iteration $k$,
we discover that all points with a Manhattan distance of $k$ from the top left
corner satisfy the invariant. Ultimately, we conclude that the bottom left
corner (i.e., $e_1 \join e_2$) satisfies the invariant and is equivalent to
$\bartu{n}{m}$.

@@

  Here's why criterion (3) is satisfied. If $s$ is an arbitrary state that
  satisfies $I$, then it is non-empty and contains, without loss of generality,
  only even integers. If $t_1$ and $t_2$ are arbitrary transactions such that
  $I(t_1(s))$ and $I(t_2(s))$, then $t_1(s)$ and $t_1(s)$ are also non-empty
  and contain only even integers. Thus, $t_1(s) \cup t_2(s)$ is clearly
  non-empty and contains only even integers, so $I(t_1(s) \join t_2(s))$.
\end{example}

>>>>

An illustration of this proof is given in \figref{DiamondProofDiagram}. We
arrange the expressions $e_1$ and $e_2$ as the left and top edges of a square
grid. Each point in the grid represents a state (with $s_0$ in the top left
corner), and each edge represents the application of a transaction. A state is
circled if we know it satisfies the invariant.
%
Condition (1) and (2) tell us that the order in which we apply transactions is
immaterial. Thus, if we begin at the top left of the square and walk to any
other point in the square, applying transactions along the way, it does not
matter which path we take. They are all equivalent. Condition (4) tells us that
the top-left corner satisfies the invariant. We induct to repeatedly apply
condition (3) to ``fill in'' the square, one block at a time. In iteration $k$,
we discover that all points with a Manhattan distance of $k$ from the top left
corner satisfy the invariant. Ultimately, we conclude that the bottom right
corner (i.e., $e_1 \join e_2$) satisfies the invariant and is equivalent to
$\bartu{n}{m}$.

@@

  Here's why criterion (3) is satisfied. If $s$ is an arbitrary state that
  satisfies $I$, then it is non-empty and contains, without loss of generality,
  only even integers. If $t_1$ and $t_2$ are arbitrary transactions such that
  $I(t_1(s))$ and $I(t_2(s))$, then $t_1(s)$ and $t_2(s)$ are also non-empty
  and contain only even integers. Thus, $t_1(s) \cup t_2(s)$ is clearly
  non-empty and contains only even integers, so $I(t_1(s) \join t_2(s))$.
\end{example}

### 2020-01-19 doc/the_vldb_journal_paper/sections/operation_based_invariant_confluence.tex
Typo fixes.

We say an expression $e$ is \defword{\sTIreachable{}} if it corresponds to a
valid execution of our system model. Formally, we define
$\sTIreachablepredicate{e}$ to be the smallest predicate that satisfies the
following equations:
\begin{itemize}
  \item
    $\sTIreachablepredicate{s_0}$.
  \item
    For all expressions $e_1, e_2$ and for all transactions $t$ in $T$, if
    $\sTIreachablepredicate{e_1}$, $\sTIreachablepredicate{e_2}$, and
    $I(t(e_1)(e_2))$, then $\sTIreachablepredicate{t(e_1)(e_2)}$.
\end{itemize}

>>>>

We say an expression $e$ is \defword{\sTIreachable{}} if it corresponds to a
valid execution of our system model. Formally, we define
$\sTIreachablepredicate{e}$ to be the smallest predicate that satisfies the
following equations:
\begin{itemize}
  \item
    $\sTIreachablepredicate{s_0}$.
  \item
    For all expressions $e_1, e_2$ and for all transactions $t$ in $T$, if
    $\sTIreachablepredicate{e_1}$, $\sTIreachablepredicate{e_2}$, and
    $I(t(e_1)(e_1))$, then $\sTIreachablepredicate{t(e_1)(e_2)}$.
\end{itemize}
